A Dependently Typed Multi-Stage Calculus

### 2019-08-26 text/formal-defnition.tex
Add some comments.

This rule is motivated by a practical consideration. We have potentially many
pairs of vectors of the fixed length in some fields, for example, computer
graphics and the same function such as vector addition is applied to all of
them. We will discuss the motivation through an example of specializing a
vector addition function with respect to the size of vectors. The function
vadd (with an auxiliary function vadd$_1$) below implements a code generator
in a hypothetical language based on \LTP. This language provides definitions
by \textbf{let}, recursive functions (represented by \textbf{fix}),
\textbf{if}-expressions, and primitives cons, head, and tail to manipulate
vectors.
We assume that
$\text{cons}$ is of type $\Pi n:\I.\I \to \text{Vector}\ n \to \text{Vector}\ (n+1)$, 
$\text{head}$ is of type $\Pi n:\I.\text{Vector}\ (n+1) \to \I$, and
$\text{tail}$ is of type $\Pi n:\I.\text{Vector}\ (n+1) \to (\text{Vector}\ n)$.

>>>>

This rule is motivated by a practical consideration. We have potentially many
pairs of vectors of the fixed length in some fields, for example, computer
graphics and the same function such as vector addition is applied to all of
them. \AK{I strenghened this example by adding concrete situation. Do we need
more reinforcements such as comparision with other method?} We will discuss
the motivation through an example of specializing a vector addition function
with respect to the size of vectors. The function vadd (with an auxiliary
function vadd$_1$) below implements a code generator in a hypothetical
language based on \LTP. This language provides definitions by \textbf{let},
recursive functions (represented by \textbf{fix}), \textbf{if}-expressions,
and primitives cons, head, and tail to manipulate vectors. We assume that
$\text{cons}$ is of type $\Pi n:\I.\I \to \text{Vector}\ n \to \text{Vector}\ (n+1)$, 
$\text{head}$ is of type $\Pi n:\I.\text{Vector}\ (n+1) \to \I$, and
$\text{tail}$ is of type $\Pi n:\I.\text{Vector}\ (n+1) \to (\text{Vector}\ n)$.
